\input{preamble}
\begin{document}
\makeheading{Tyler W. Rinker}

\section{Contact Information}


\newlength{\rcollength}\setlength{\rcollength}{2.1in}%
\newlength{\spacewidth}\setlength{\spacewidth}{20pt}
\begin{tabular}[t]{@{}p{\textwidth-\rcollength-\spacewidth}@{}p{\spacewidth}@{}p{\rcollength}}%

% Address box
\parbox{\textwidth-\rcollength-\spacewidth}{%
\href{http://www.buffalo.edu/}{University at Buffalo, SUNY}\\
Graduate School of Education\\
Department of Learning and Instruction\\	
510 Baldy Hall\\
Buffalo, NY 14260-1000\\}

&
% Uncomment to add a vertical bar in middle of contact information
%{\vrule width 0.5pt}
\parbox[m][5\baselineskip]{\spacewidth}{} &

% Non-snail-mail contact information
\parbox{\rcollength}{%
\textit{Mobile:} 1-716-472-2642 \\
\textit{Office:} 1-716-645-4042 \\
\textit{E-mail:} \email{tyler.rinker@gmail.com}\\
\textit{Web:} \href{http://about.me/tylerrinker}{about.me/tylerrinker}}

\end{tabular}

\section{Education}

\href{http://www.buffalo.edu/}{\textbf{University at Buffalo, SUNY}}
Buffalo, NY
\begin{outerlist}

\item[] Ph.D.,
        \href{http://gse.buffalo.edu/lai/doc}
             {Reading Education},
             \emph{Expected:} Summer 2015
        \begin{innerlist}
        \item Adviser:
              \href{http://gse.buffalo.edu/about/directory/faculty/2110}
                   {Lynn E. Shanahan, Ph.D.}
        \end{innerlist}
\end{outerlist}
\vspace{.1in}

\href{http://www.buffalostate.edu/}{\textbf{Buffalo State College, SUNY}}
Buffalo, NY
\begin{outerlist}

\item[] C.A.S.,
        \href{http://www.buffalostate.edu/gradprog.xml?bpid=27}
             {Educational Leadership},
             Spring 2009
        \begin{innerlist}
        \item Adviser:
              \href{http://elementaryeducation.buffalostate.edu/faculty/nancy-chicola}
                   {Nancy Chicola, Ph.D.}
        \end{innerlist}
\end{outerlist}
\vspace{.1in}

\begin{outerlist}

\item[] M.S.,
        \href{http://www.buffalostate.edu/gradprog.xml?bpid=27}
             {Childhood \& Early Childhood Curriculum \& Instruction},
             Spring 2007
\end{outerlist}
\vspace{.1in}

\href{http://www.houghton.edu/}{\textbf{Houghton College}}
Buffalo, NY
\begin{outerlist}

\item[] B.S.,
        \href{http://www.houghton.edu/education/}
             {Elementary Education},
             Spring 2002
\end{outerlist}
\vspace{.1in}


\section{Research Experience}

\textbf{Research Project Manager} \hfill {Sept 2012 to present}
\begin{innerlist}

\item[] \href{http://clari.buffalo.edu}{Center for Literacy and Reading Instruction},\\
        University at Buffalo, SUNY\\
        Supervisor: Mary M. McVee, Ph.D.
\end{innerlist}

\textbf{Graduate Assistant} \hfill {Sept 2010 to Jan 2011}
\begin{innerlist}

\item[] Department of Learning and Instruction,\\
        University at Buffalo, SUNY\\
        Supervisors: Lynn E. Shanahan, Ph.D.
\end{innerlist}

\section{Relevant Courses}

CEP 528 Hierarchical Linear Models (HLM): Multilevel and Longitudinal Data Analysis\\
CEP 524 Experimental Design in Educational Research\\
CEP 530 Introduction to Meta-Analysis\\
LAI \hspace{1mm}657 Analysis of Quantitative Research I\\
CEP 510 Psychometric Theory in Education\\
CEP 529 Applied Regression Analysis\\
CEP 523 Statistical Methods: Inference II\\
CEP 522 Statistical Methods: Inference I\\


\section{Submitted Journal Publications}
\vspace{-.1275in}
\begin{bibsection}
    \item Aloe, A. M., Shisler, S. M., Norris, B. D., Nickerson, A. B., \& Rinker, T. W. (2014). A multivariate meta-analysis of student misbehavior and teacher burnout. \emph{Educational Research Review}. Manuscript submitted for publication.
\end{bibsection}


\halfblankline

\section{Papers in Preparation}
\vspace{-.1in}
\begin{bibsection}

\item Erekson, J., McVee, M. B., Rinker, T. W., \& et al. (2013). \emph{Ten best ideas for reading teachers: A retrospective analysis}. Paper presented at the Literacy Research Association, Dallas, TX.

\item Rinker, T. W. and McVee, M. B. (2013).  \emph{Student Engagement with Mediational Tools in a Literacy Clinic: A Multimodal Examination of Clinician Designed Materials}.  Paper presented at the Literacy Research Association, Dallas, TX.
\end{bibsection}

\halfblankline


\halfblankline


\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%
