\input{preamble}
\begin{document}
\makeheading{Tyler W. Rinker}

\section{Contact Information}


\newlength{\rcollength}\setlength{\rcollength}{2.1in}%
\newlength{\spacewidth}\setlength{\spacewidth}{20pt}
\begin{tabular}[t]{@{}p{\textwidth-\rcollength-\spacewidth}@{}p{\spacewidth}@{}p{\rcollength}}%

% Address box
\parbox{\textwidth-\rcollength-\spacewidth}{%
\href{http://www.buffalo.edu/}{University at Buffalo, SUNY}\\
Graduate School of Education\\
Department of Learning and Instruction\\	
510 Baldy Hall\\
Buffalo, NY 14260-1000\\}

&
% Uncomment to add a vertical bar in middle of contact information
%{\vrule width 0.5pt}
\parbox[m][5\baselineskip]{\spacewidth}{} &

% Non-snail-mail contact information
\parbox{\rcollength}{%
\textit{Mobile:} 1-716-472-2642 \\
\textit{Office:} 1-716-645-4042 \\
\textit{E-mail:} \email{tyler.rinker@gmail.com}\\
\textit{Web:} \href{http://about.me/tylerrinker}{about.me/tylerrinker}}

\end{tabular}

\section{Research Interests}

Development of literacy research methods, data visualization, discourse analysis, new literacies/multimodality, classroom student engagement, and teacher professional development.

\section{Education}

\href{http://www.buffalo.edu/}{\textbf{University at Buffalo, SUNY}}
Buffalo, NY
\begin{outerlist}

\item[] Ph.D.,
        \href{http://gse.buffalo.edu/lai/doc}
             {Reading Education},
             \emph{Expected:} Summer 2015
        \begin{innerlist}
        \item Thesis Topic: \emph{UNKNOWN}
        \item Adviser:
              \href{http://gse.buffalo.edu/about/directory/faculty/2110}
                   {Lynn E. Shanahan, Ph.D} 
        \end{innerlist}
\end{outerlist}
\vspace{.1in}

\href{http://www.buffalostate.edu/}{\textbf{Buffalo State College, SUNY}}
Buffalo, NY
\begin{outerlist}

\item[] C.A.S.,
        \href{http://www.buffalostate.edu/gradprog.xml?bpid=27}
             {Educational Leadership},
             Spring 2009
        \begin{innerlist}
        \item Adviser:
              \href{http://elementaryeducation.buffalostate.edu/faculty/nancy-chicola}
                   {Nancy Chicola, Ph.D} 
        \end{innerlist}
\end{outerlist}
\vspace{.1in}

\begin{outerlist}

\item[] M.S.,
        \href{http://www.buffalostate.edu/gradprog.xml?bpid=27}
             {Childhood \& Early Childhood Curriculum \& Instruction},
             Spring 2007
\end{outerlist}
\vspace{.1in}

\href{http://www.houghton.edu/}{\textbf{Houghton College}}
Buffalo, NY
\begin{outerlist}

\item[] B.S.,
        \href{http://www.houghton.edu/education/}
             {Elementary Education},
             Spring 2002
\end{outerlist}
\vspace{.1in}


\section{Research Experience}

\textbf{Research Project Manager} \hfill {Sept 2012 to present}
\begin{innerlist}

\item[] \href{http://clari.buffalo.edu}{Center for Literacy and Reading Instruction},\\
        University at Buffalo, SUNY\\
        Supervisor: Mary M. McVee, Ph.D
\end{innerlist}

\textbf{Graduate Assistant} \hfill {Sept 2010 to Jan 2011}
\begin{innerlist}

\item[] Department of Learning and Instruction,\\
        University at Buffalo, SUNY\\
        Supervisors: Lynn E. Shanahan, Ph.D
\end{innerlist}

\section{Refereed Journal Publications}
\vspace{-.1275in}
\begin{bibsection}
    \item Aloe, A. M., Shisler, S. M., Norris, B. D., Nickerson, A. B., \& Rinker, T. W. (in press). A multivariate meta-analysis of student misbehavior and teacher burnout. \emph{Educational Research Review}.
    \item McVee, M. B., McGrath, K., \& Rinker, T. W. (in press). A phenomenological study of narrative interviews with parents of struggling readers: Bringing parent voices into the academy. \emph{Research Reading Quarterly}.
\end{bibsection}

\halfblankline

\section{Book Chapters}
\vspace{-.1275in}
\begin{bibsection}
    \item Shanahan, L. E., McVee, M. B., Schiller, J. A., Tynan, E. A., D'Abate, R. L., Flury-Kashmanian, C. M., Rinker, T. W., Ebert, A. A., \& Hayden, H. E. (2013). Learning to support struggling readers and literacy clinicians through reflective pedagogy. In E. Ortlieb \& E. Cheek, Jr. (Eds.), \emph{Literacy research, practice, and evaluation}. Corpus Christi: Emerald Press.
\end{bibsection}

\section{Submitted Journal Publications}
\vspace{-.125in}
\begin{bibsection}
    \item 
\end{bibsection}


\halfblankline

\section{Papers in Preparation}
\vspace{-.1in}
\begin{bibsection}
    \item Shanahan, L. E., Tochelli, A. L., \& Rinker, T. W.(2013). Teacher growth in explicit strategy 
instruction. (Presentation for the Literacy Research Association Annual Conference \& Related Article Submission).

    \item McVee, M. B., Brock, C., Rinker, T. W, \& et al. (2013). 10 best ideas for reading: An 
analysis of Fry's text. (Presentation for the Literacy Research Association Annual Conference) 

\end{bibsection}

\section{Awards}
\begin{innerlist}
\item William C. Eller Memorial Scholarship\hfill 2012-2013
\end{innerlist}

\halfblankline

\section{Presentations}
National Presentations
\begin{innerlist}
\item Rinker, T. W., McVee, M. B., Cho, Y. and Schiller, J. A. (2012, November).  \emph{The Overlooked Role of Teacher Feedback During Literacy Instruction: Tensions Between Engagement, Embodiment, and Ipseity}.  Paper presented at the Literacy Research Association, San Diego, CA.

\item Rinker, T. W. and McVee, M. B. (2013, December).  \emph{Student Engagement with Mediational Tools in a Literacy Clinic: A Multimodal Examination of Clinician Designed Materials}.  Paper presented at the Literacy Research Association, Dallas, TX.
\end{innerlist}

\halfblankline

Professional Presentations: Invited
\begin{innerlist}
    \item Rinker, T. W. (2013, December). \href{http://rpubs.com/trinker/11429}{qdap Demonstration: If You Can Dream up an Analysis then qdap and R Can Help Get You There}.  Presented for \href{http://www.buffalo.edu/ria.html}{Research Institute on Addictions}.
    \item Rinker, T. W. (2013, September). Affordances of HTML5 in Academic Writing: A Tool to Enhance the Interaction With and Presentation of Data.  Presented for \href{http://gse.buffalo.edu/org/nlg/}{New Literacies Group} at University at Buffalo, SUNY.
    \item Rinker, T. W. (2013, June). \href{http://www.youtube.com/watch?v=IHHPO4VhucY}{Data Visualization: Seeing the Story in the Data and Learning to Effectively Communicate It to Others}.  Presented for CLaRI 50th Anniversary Literacy Conference: Looking Back, Moving Forward, at University at Buffalo, SUNY.
	\item Rinker, T. W. (2013, February). Quantitative Discourse Analysis and Visualization. Presented for LAI 626: Discourse Analysis, at University at Buffalo, SUNY.
	\item Rinker, T. W. (2012, November). Qualitative Data Analysis and Writing. Presented for LAI 659: Qualitative Techniques for Education, at University at Buffalo, SUNY.
	\item Rinker, T. W. (2012, February). Quantitative Discourse Analysis and Visualization. Presented for LAI 626: Discourse Analysis, at University at Buffalo, SUNY.
\end{innerlist}

\section{Teaching Experience}

%\textbf{Teaching Assistant} \hfill {Springs 2011--12}
Co-instructor \hfill {Spring 2013}
\begin{innerlist}
\item[] LAI 556 - Classroom-Based Literacy Assessment\\
        with Lynn E. Shanahan\\
        Department of Learning and Instruction,\\
        University at Buffalo, SUNY
\end{innerlist}

\section{Computer Software Development}
Computer and Document Languages:
%
\begin{innerlist}
    \item R, \LaTeX, HTML, CSS, R Markdown 
\end{innerlist}

\halfblankline

Program Development
\begin{innerlist}
    \item Rinker, T. W. (2013). \href{http://cran.r-project.org/web/packages/qdap/index.html}{qdap: Quantitative Discourse Analysis Package}. version 0.2.1. University at Buffalo. Buffalo, New York. \url{http://github.com/trinker/qdap}
    \item Rinker, T. W. (2013). \href{http://cran.r-project.org/web/packages/reports/index.html}{reports: Package to assist in report writing}. version 0.1.0. University at Buffalo. Buffalo, New York. \url{http://github.com/trinker/reports}
    \item Rinker, T. W. \& Kurkiewicz, D. (2013). pacman: Package Management for R version 0.2.0. University at Buffalo. Buffalo, New York. \url{http://github.com/trinker/pacman}
    \item Rinker, T. W. \& Aloe, A. M. (2013). metaDAT: Meta-analysis data management tool. version 0.1.0. University at Buffalo. Buffalo, New York. \\ \url{http://github.com/trinker/metaDAT}
\end{innerlist}

\section{Service}

\begin{innerlist}
    \item Literacy Research Association Conference Reviewer \hfill {2013}
\end{innerlist}



\section{Professional Memberships}
\begin{innerlist}
    \item \href{http://www.literacyresearchassociation.org/}{Literacy Research Association}\hfill {Sept 2012 -- Present}
    \item \href{http://www.reading.org/}{International Reading Association}\hfill {Jan 2013 -- Present}
\end{innerlist}


\section{References}
\href{http://gse.buffalo.edu/about/directory/faculty/2039}{Mary B. McVee}
\begin{innerlist}
\item[] Associate Professor \&
\item[] Director of the Center for Literacy and Reading Instruction \hfill {Phone: 716-645-2458}\\
Department of Learning and Instruction \hfill{E-mail: \href{mailto:mcvee@buffalo.edu}{\nolinkurl{mcvee@buffalo.edu}}}\\
University at Buffalo
\end{innerlist}

\href{http://gse.buffalo.edu/about/directory/faculty/2110}{Lynn E. Shanahan}
\begin{innerlist}
\item[] Assistant Professor \hfill {Phone: 716-645-4028}\\
Department of Learning and Instruction \hfill{E-mail: \href{mailto:ls34@buffalo.edu}{\nolinkurl{ls34@buffalo.edu}}}\\
University at Buffalo
\end{innerlist}
\halfblankline


\halfblankline


\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%% End CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%%